\texttt{Davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-10-01 paper/main.tex
add zenodo link to metadata table
added zenodo link to meta-data table, added explicit discussion of lockfiles and Poetry

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata value} \\
\hline
C1 & Current code version &  v0.2.3 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.2.3} \\
\hline
C3 & Code Ocean compute capsule & \\
\hline
C4 & Legal Code License & MIT \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, ipykernel, PyZMQ.\newline Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
\hline
C7 & Compilation requirements, operating environments, and
     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.\newline Supported OSes: MacOS, Linux, Unix-like.\newline Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, Kaggle, IDE-based notebook editors, IPython shell. \\
\hline
C8 & Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
\hline
C9 & Support email for questions & \href{mailto:contextualdynamics@gmail.com}{contextualdynamics@gmail.com} \\
\hline
\end{tabular}
\caption{Code metadata}
\label{}
\end{table}

@@

A second limitation of \texttt{Davos} relates to how packages are installed and managed.
As of this writing, \texttt{Davos} can install packages using \texttt{pip}, but not
other standard Python package management systems such as \texttt{conda}~\cite{Anac12}.
Therefore packages that are not installable via \texttt{pip} are currently
unsupported by \texttt{Davos}. We anticipate adding support for other package management
systems, including \texttt{conda}, in a future release.

>>>>

\begin{table}[H]
  \footnotesize
\begin{tabular}{|l|p{6cm}|p{8cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata value} \\
\hline
C1 & Current code version &  v0.2.3 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://doi.org/10.5281/zenodo.8233890} \\
\hline
C3 & Code Ocean compute capsule & N/A\\
\hline
C4 & Legal Code License & MIT \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, ipykernel, PyZMQ.\newline Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
\hline
C7 & Compilation requirements, operating environments, and
     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.\newline Supported OSes: MacOS, Linux, Unix-like.\newline Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, Kaggle, IDE-based notebook editors, IPython shell. \\
\hline
C8 & Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
\hline
C9 & Support email for questions & \href{mailto:contextualdynamics@gmail.com}{contextualdynamics@gmail.com} \\
\hline
\end{tabular}
\caption{Code metadata}
\label{}
\end{table}

@@

A second limitation of \texttt{Davos} relates to how packages are installed and managed.
As of this writing, \texttt{Davos} can install packages using \texttt{pip}, but not
other standard Python package management systems such as \texttt{conda}~\cite{Anac12}.
Therefore packages that are not installable via \texttt{pip} are currently
unsupported by \texttt{Davos}. We anticipate adding support for other package management
systems, including \texttt{conda}, in a future release.  Because \texttt{Davos} relies on
\texttt{pip} to install packages, it is also subject to the same limitations as
\texttt{pip} itself. For example, \texttt{pip}-installing a package that depends on
a previously \texttt{smuggle}d package may result in the previously smuggled package
being upgraded or downgraded to a different version. Whereas lockfiles, or lockfile-based
systems like \texttt{Poetry}~\citep{poetry}, place stronger guarantees that each package will
have a stable version, we have opted for a more flexible (but, consequently, less
deterministic) implementation for \texttt{Davos}.  This enables us to support
more advanced use cases, such as those described in Section~\ref{sec:illustrative-example},
but at the cost of managing potential conflicts between \texttt{smuggle}d
packages.
